An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-06-07 poly-embed-journal/poly-embed-journal.tex
pass on E

\section{General characteristics of polyhedra}
\label{app:polyhedra}
\subsection{General definitions for polyhedra}
\label{app:polyhedra:defs}
\begin{definition}[Closed halfspace]
  A closed halfspace is a set of the form $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} \geq b\}$ for some $(w,b) \in \reals^d \times \reals$.
  % Similarly let $H_{(w,b)}^- := \{ x \in \reals^d \mid \inprod{x}{w} \leq b\}$.
\end{definition}
\begin{definition}[Hyperplane]
  A hyperplane is a set of the form $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} = b\}$ for some $(w,b)\in\reals^d \times \reals$.
  % The halfspaces corresponding to a hyperplane $H = H_{(w,b)}$ are the sets $H_{(w,b)}^+$ and $H_{(w,b)}^-$.
\end{definition}

@@

While one traditionally considers $P$ to be a trivial face of itself, we exclude this case throughout by discussing nontrivial faces.
\raft{It was a bit confusing because you said to observe that $P$ was a face of itself when you defined face to exclude that possibility\jessie{Is this clearer?}}

@@

\begin{definition}[Adapted from {\citet{gallier2008notes}}]\label{def:irredundant}
	Let $P = \cap \H$ for a finite set of closed halfspaces $\H$ be a polyhedron.
	We say that $\cap \H$ is an \emph{irredundant decomposition} for $P$ (and $\H$ is irredundant for $P$) if $P$ cannot be expressed as $P = \cap \H'$ for some set of closed halfspaces $\H'$ such that $|\H'| < |\H|$, and redundant otherwise.
	If $\cap \H'$ is an irredundant decomposition of $P$, then we call $\partial H^+$ an irredundant face of $P$ for each $H^+ \in \H'$.\jessiet{Added this sentence but not sure if it's necessary anymore.}
\end{definition}

@@

\begin{theorem}[{\citet{gallier2008notes}}]\label{thm:polyhedron-uniquely-gen-facets}
  Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, 
  (i) there is a unique irredundant and finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, 
  (ii) $\{H \cap P \mid H^+ \in \H^*, H = \partial H^+\}$ is the set of facets of $P$, and
  (iii) for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$.
\end{theorem}
\begin{proof}
	Since $P$ is $d$-dimensional in $\reals^d$, it therefore has nonempty interior.
	As $P$ has a finite halfspace representation, it must have a smallest halfspace representation $\H^*$.
	That is, $|\H^*| = \min \{|\H| : P = \cap \H, \H$ finite$\}$.
	As the smallest halfspace representation, $\H^*$ is irredundant by definition.
%	Since $P$ has a (finite) halfspace representation, if any representation $\cap \H$ was redundant, then its redundant representation would either be irredundant or have a smaller representation.
%	This can only iterate up to $|\H^*|$ times, so there must be some finite irredunant representation for $P$.\jessie{This feels way too spelled out for its lack of detail.}
	\citet[Proposition 4.5(i)]{gallier2008notes} then states that $\H^*$ is unique, giving (i).
	Additionally, (ii) is shown by~\citep[Proposition 4.5(ii)]{gallier2008notes}.

	\jessiet{Took a pass}
	It remains to show (iii).
  Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.
  By (ii), each $H^+ \in \H^*$  determines a facet of $P$, and this facet is irredundant by (i)\raft{Not defined (I think) what it means for a facet to be irredundant.  \jessie{good catch; updated the definition. burn.}}.
  If $H^+ \not \in \H$, then $\cap \H \neq P$ as convex polytopes are uniquely determined by their facets (cf.~\citep[pg. 455]{schneider2014convex})\raft{This citation is doing the heavy lifting---what exactly does it say?}, a contradiction.
  Therefore, we must have $H^+ \in \H$ as well.
	%Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
%	By (i), we know that each $H^+ \in \H^*$ uniquely determines a facet of $P$.
%	Moreover, by (ii), define $F := P \cap H$, where $H = \partial H^+$ and $H^+ \in \H^*$, which is a facet of $P$ and of dimension $d-1$.
%	As halfspaces are uniquely determined, so is the facet $F = P \cap H$.
%	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem, cf.,~\citep{klain2004minkowski}), we must have $H^+ \in \H$. 
%	\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}

@@

Given any $v \in \reals^\Y_+$, define $H^+_v := H^+_{(v, -1)} = \{(x, c) \in \reals^{\Y}_+ \times \reals \mid \inprod{v}{x} = c\}$.
%, where $(v, -1)\in\reals^\Y_+\times\reals$ defines a halfspace.
Similarly, we denote $H_y^+ := H_{(e_y, 0)}^+$ for any $y \in \Y$; the latter will help us restrict a constructed polyhedron to the nonnegative orthant. 
Extending to hyperplanes, we construct $H_v := H_{(v,-1)}$ and observe that $H_v = \partial H^+_v$ for $v \in \reals^\Y_+$ and define $H_y := H_{(e_y, 0)}$ so that $H_y = \partial H^+_y$.

Given a set $\V \subseteq \reals^d$, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$.
%If $\V$ and $\Y$ are understood from context, we may denote $\H := \H_\V \cup\H_\Y$.

For any $S \subseteq \reals^k$, let $\delta(\cdot \mid S):\reals^k \to \reals \cup \{\infty\}$ be the convex indicator function, given by $\delta(x \mid S) = 0$ if $x\in S$ and $\infty$ otherwise.
Throughout, we will work with a function $g_\V$ generated by a set $\V \subseteq \reals^\Y_+$ of the following form, often polyhedral (but concave).
%Intuitively, one can think of $g_\V$ as a Bayes risk, where $\V$ is the report set, and the input acts like a label distribution.

\begin{definition}\label{def:g-finite}
  Given a set $\V \subseteq \reals^\Y_+$, define the function $g_\V : \reals_+^\Y \to \reals_+$ by
  \begin{align*}
    g_\V(x) = \inf_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~. % = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~.~
  \end{align*}
\end{definition}
\noindent
We denote the hypograph of $g_\V$ by $\hyp(g_\V) = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$.

@@

Using the polyhedral perspective above, we can characterize the hypograph of $\risk L_+ = g_{L(\R)}$ and extract a \emph{finite} set $\V$ of ``active'' loss vectors, so that $\risk L_+ = g_\V$.
%Let $\H_{L(\R)} = \{H_v^+ \mid v\in L(\R)\}$.
Observe that $L(\R)$ and $\H_{L(\R)}$ may be infinite sets.  
\raft{FYI, I have seen tons of places where you defined things in the text, and then again in the claim/lemma/theorem statement, which actually makes it more confusing.  Probably a hold-over from when you only defined things out of statements}
%We find the existence of a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$, and proceed to work with such a $\V$.
\begin{claim}\label{claim:gV-equals-riskL}
	Suppose we are given a minimizable $L : \R \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$.
	Then $\hyp(g_{L(\R)}) = \cap(\H_\Y \cup \H_{L(\R)})$.
	Moreover, there is a finite $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_{\V}$. %$\hyp(g_{L(\R)}) = \cap (\H_{\V} \cup \H_\Y) = \hyp(g_{\V})$ and . 
\end{claim}
\begin{proof}
	Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
	Let $x \in \reals^\Y_+$.
	\begin{align*}
	(x,c) \in \hyp(g_{L(\R)})
	&\iff g_{L(\R)}(x) \geq c & \text{ Definition of hypograph;}\\
	&\iff \risk L_+(x) \geq c & \text{$g_{L(\R)}=\risk L_+$;}\\
	&\iff \inprod{v}{x} \geq c \,\, \forall v \in {L(\R)} & \text{by def of $\risk L_+$ as the infimum over $v \in {L(\R)}$ of}\\
	& & \text{the inner product with $x$ and minimizable;} \\
	&\iff (x,c) \in H^+_{v} \,\, \forall v \in {L(\R)} & \text{by definition of each halfspace;}\\
	&\iff (x,c) \in \cap \H_{L(\R)} & \text{since true for all $v \in {L(\R)}$.}  
	\end{align*}
	Combining the two equalities, we have $\hyp(g_{L(\R)}) = \cap (\H_\Y \cup \H_{L(\R)})$.
	The existence of a finite $\V \subseteq {L(\R)}$ follows as $\risk L_+$ polyhedral implies $\hyp(\risk L_+)$ is a polyhedron, which has a finite representation by definition. \jessiet{Omitting details on why $\V \subseteq {L(\R)}$.}
	%Finally, $\hyp(\risk L_+) = \hyp(g_{L(\R)}) = \hyp(g_{\V})$ if and only if $\risk L_+ = g_{L(\R)} = g_{\V}$. 
\end{proof}

@@

The previous claim allows us to proceed while considering the finite set $\V$ rather than the full range $L(\R)$.
We now evaluate the structure of $g_{L(\R)} = g_\V$ and its hypograph through $\V$.
%We will work with any $\V \subseteq \reals^\Y_+$ which is finite.
%Now, we can define $\hyp(g_\V)$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
%\jessie{This isn't reffed anywhere else in the paper.  Remove?}
%\begin{claim}\label{claim:G-intersection-H}
%  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$.
%  Then $\hyp(g_\V) = \cap \H$.
%\end{claim}
%\begin{proof}
%  $(x,c) \in \hyp(g_\V) \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
%  In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
%\end{proof}

\jessie{We want to get to $\V^*$.  We need to build up to it through $\V$ and working with extended BR.}
We proceed with some observations about facets and dimension of $\hyp(g_\V)$ in order to use the \emph{smallest} halfspace representation $\H^*$ for $g_{L(\R)} = g_\V$.

%\jessiet{Move into next lemma?  it's only used that one time, and it's so short it might as well go in.- June 2}
%\begin{lemma}\label{lem:G-full-dimensional}
%  Given a finite, nonempty set $\V \subset \reals^\Y_+$, $\hyp(g_\V)$ is $d$-dimensional.  %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.} 
%\end{lemma}
%\begin{proof}
%  Since $g_\V$ is nonnegative on $\reals_+^\Y$, $\hyp(g_\V)$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
%  Recall $d= (|\Y| + 1)$.
%\end{proof}

\jessiet{move theorem~\ref{thm:polyhedron-uniquely-gen-facets} here?- June 2}

With a bit of preliminary work, we can apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets} to observe a unique irredundant halfspace representation $\H^*$ generating $\hyp(g_\V)$.

\jessie{Getting to $\V^*$ through $\H^*$, which exists (and contains $\H_\Y$)}
\begin{lemma}\label{lem:G-unique-facets-Hstar}
  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$.
  %\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
  There is some unique irredundant $\H^* \subseteq \H$ such that $\hyp(g_\V) = \cap \H^*$. 
  Moreover, for each $H^+ \in\H^*$ and $H$ such that $H = \partial H^+$, the face $\hyp(g_\V) \cap H$ is a facet. 
  Moreover, $\H_\Y \subseteq \H^*$. 
\end{lemma}
\begin{proof}
	First, we need to show that $\hyp(g_\V)$ is full-dimensional.
	Since $g_\V$ is nonnegative on $\reals_+^\Y$, $\hyp(g_\V)$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.

@@

\begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
  Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ given by Lemma~\ref{lem:G-unique-facets-Hstar}. %such that $\hyp(g_\V) = \cap \H^*$.
  Then
  (i) There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  (ii)$F_v$ is a facet of $\hyp(g_\V)$ for each $v\in\V^*$.
  (iii) $\V^* \subseteq \V$.
\end{corollary}
\begin{proof}
%  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
%
  (i) Since $\hyp(g_\V)$ is full-dimensional, the facets of $\hyp(g_\V)$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $H^+ \in \H^*$\raft{was ``$\H^* = \{H^+\}$''} by Lemma~\ref{lem:G-unique-facets-Hstar}.
  Any facet must then be some intersection of an $H_y \cap \hyp(g_\V)$ or $H_v \cap \hyp(g_\V)$.
  Since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}, take $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$.
  (ii) Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v$ of $\hyp(g_\V)$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
%
%  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Lemma~\ref{lem:G-unique-facets-Hstar}.
  (iii)  $\H_\Y \cup \H_{\V^*} = \H^*$ by (i), and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:G-unique-facets-Hstar}, ergo $\V^* \subseteq \V$.
\end{proof}

@@

We now show that we can equivalently construct $g_\V$ through the unique finite set $\V^*$ instead of the given set of vectors $\V$, and and later, extend this result to loss vectors $L(\R)$.
\begin{lemma}\label{claim:g-gen-by-Vstar}
	Given a finite set $\V \subset \reals^\Y_+$, consider $\V^* \subseteq \V$ as in Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}.
  Then $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$
\end{lemma}
\begin{proof}
  The result holds if $\hyp(g_\V) = \hyp(g_{\V^*})$.
  By construction, $\hyp(g_\V) = \cap (\H_\Y \cup \H_\V)= \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
  This means $g_\V$ can be written as $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+) = g_{\V^*}(x)$. 
\end{proof}

This paves the way for our primary assumption for the rest of this appendix, which we show is always satisfied by losses with polyhedral extended risk.

\begin{assumption}\label{assum:V-star-exists-infinite}
	$L : \R \to \reals^\Y_+$ is a minimizable loss function such that $\risk L_+ = g_{L(\R)}$ is polyhedral.
	%$\V \subseteq L(\R)$ is a finite set such that $g_\V = g_{L(\R)}$.
	$\V^* \subseteq L(\R)$ is the unique finite set such that $g_{L(\R)} = g_{\V^*}$ and $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap(\H_{\V^*} \cup \H_\Y)$, and the last of these is irredundant.
\end{assumption}

\begin{proposition}\label{prop:poly-risk-assumption-satisfied}
	Given a minimizable loss $L : \R \to \reals^\Y_+$ such that $\risk L_+$ is polyhedral, there exists a finite $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
\end{proposition}
\begin{proof}
	\jessie{Can use careful eyes}
	Given $L$ with polyhedral $\risk L_+$, Claim~\ref{claim:gV-equals-riskL} gives a finite set $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_\V$. 
	Now consider the unique $\V^* \subseteq \V \subseteq L(\R)$ that is given in Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $g_{L(\R)} = g_\V = g_{\V^*}$.
	Equality of the hypographs follows immediately from equailty of the graphs.
	Finally, by construction in Lemma~\ref{lem:G-unique-facets-Hstar}, we additionally have $\H^* = \H_\Y \cup \H_{\V^*}$, and $\cap \H^*$ is irredundant.
%	WTS
%	(i) $\V^* \subseteq L(\R)$ -- done
%	(ii) $\V^*$ unique and smallest
%	(iii) $g_{L(\R)} = g_{\V^*}$
%	(iv) $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap (\H_{\V^*} \cup \H_\Y)$
\end{proof}

>>>>

\section{General characteristics of polyhedra}
\label{app:polyhedra}

In this section, we give a careful treatment of the results on convex polyhedra needed to prove Lemma~\ref{lem:X}.

\subsection{General definitions for polyhedra}
\label{app:polyhedra:defs}

We begin with general definitions of polyhedra.
See also \raf{cite Ziegler} and \citet{gallier2008notes}.

\begin{definition}[Closed halfspace]
  A closed halfspace is a set of the form $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} \geq b\}$ for some $(w,b) \in \reals^d \times \reals$.
  % Similarly let $H_{(w,b)}^- := \{ x \in \reals^d \mid \inprod{x}{w} \leq b\}$.
\end{definition}
\begin{definition}[Hyperplane]
  A hyperplane is a set of the form $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} = b\}$ for some $(w,b)\in\reals^d \times \reals$.
  % The halfspaces corresponding to a hyperplane $H = H_{(w,b)}$ are the sets $H_{(w,b)}^+$ and $H_{(w,b)}^-$.
\end{definition}

@@

While one traditionally considers $P$ to be a trivial face of itself, we exclude this case throughout.

@@

\begin{definition}[Irredundant; adapted from {\citet{gallier2008notes}}]\label{def:irredundant}
	Let $P = \cap \H$ for a finite set of closed halfspaces $\H$ be a polyhedron.
	We say that $\cap \H$ is an \emph{irredundant decomposition} for $P$ (and $\H$ is irredundant for $P$) if $P$ cannot be expressed as $P = \cap \H'$ for some set of closed halfspaces $\H'$ such that $|\H'| < |\H|$, and redundant otherwise.
\end{definition}

@@

\begin{theorem}[{\citet{gallier2008notes}}]\label{thm:polyhedron-uniquely-gen-facets}
  Given a $d$-dimensional polyhedron $P \subseteq \reals^d$, 
  (i) there is a unique irredundant and finite set of closed halfspaces $\H^*$ such that $P = \cap \H^*$, 
  (ii) $\{H \cap P \mid H^+ \in \H^*, H = \partial H^+\}$ is the set of facets of $P$, and
  (iii) for all finite sets of closed halfspaces $\H$ such that $P = \cap \H$, we have $\H^* \subseteq \H$.
\end{theorem}
\begin{proof}
	Since $P$ is $d$-dimensional in $\reals^d$, it therefore has nonempty interior.
	As $P$ has a finite halfspace representation, it must have a smallest halfspace representation $\H^*$.
	That is, $|\H^*| = \min \{|\H| : P = \cap \H, \H$ finite$\}$.
	As a smallest halfspace representation, $\H^*$ is irredundant by definition.
%	Since $P$ has a (finite) halfspace representation, if any representation $\cap \H$ was redundant, then its redundant representation would either be irredundant or have a smaller representation.
%	This can only iterate up to $|\H^*|$ times, so there must be some finite irredunant representation for $P$.\jessie{This feels way too spelled out for its lack of detail.}
	\citet[Proposition 4.5(i)]{gallier2008notes} then states that $\H^*$ is unique, giving (i).
	Additionally, (ii) is shown by~\citep[Proposition 4.5(ii)]{gallier2008notes}.

	It remains to show (iii).
  Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.
  By (ii), each $H^+ \in \H^*$  determines a facet of $P$.
  If $H^+ \not \in \H$, then $\cap \H \neq P$ as convex polytopes are uniquely determined by their facets (cf.~\citep[pg. 455]{schneider2014convex})\raft{This citation is doing the heavy lifting---what exactly does it say?}, a contradiction.
  Therefore, we must have $H^+ \in \H$ as well.
	%Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
%	By (i), we know that each $H^+ \in \H^*$ uniquely determines a facet of $P$.
%	Moreover, by (ii), define $F := P \cap H$, where $H = \partial H^+$ and $H^+ \in \H^*$, which is a facet of $P$ and of dimension $d-1$.
%	As halfspaces are uniquely determined, so is the facet $F = P \cap H$.
%	As polyhedron are uniquely determined by their facets (by Minkowski's uniqueness theorem, cf.,~\citep{klain2004minkowski}), we must have $H^+ \in \H$. 
%	\jessiet{This is not as precise as I'd like... but also I think it follows more immediately from Minkowski's uniqueness theorem}

@@

Given any $v \in \reals^\Y_+$, define $H^+_v := H^+_{(v, -1)} = \{(x, c) \in \reals^{\Y}_+ \times \reals \mid \inprod{v}{x} = c\}$.
%, where $(v, -1)\in\reals^\Y_+\times\reals$ defines a halfspace.
Similarly, we denote $H_y^+ := H_{(e_y, 0)}^+$ for any $y \in \Y$; the latter will help us restrict a constructed polyhedron to the nonnegative orthant. 
Extending to hyperplanes, we construct $H_v := H_{(v,-1)}$ and observe that $H_v = \partial H^+_v$ for $v \in \reals^\Y_+$ and define $H_y := H_{(e_y, 0)}$ so that $H_y = \partial H^+_y$.
Given a set $\V \subseteq \reals^d$, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$.
Similarly, let $\H_\Y = \{H_y^+ \mid y\in\Y\}$.
%If $\V$ and $\Y$ are understood from context, we may denote $\H := \H_\V \cup\H_\Y$.

For any $S \subseteq \reals^k$, let $\delta(\cdot \mid S):\reals^k \to \reals \cup \{\infty\}$ be the convex indicator function, given by $\delta(x \mid S) = 0$ if $x\in S$ and $\infty$ otherwise.
Throughout, we will work with a concave function $g_\V$ generated by a set $\V \subseteq \reals^\Y_+$ of the following form.
%Intuitively, one can think of $g_\V$ as a Bayes risk, where $\V$ is the report set, and the input acts like a label distribution.

\begin{definition}\label{def:g-finite}
  Given a set $\V \subseteq \reals^\Y_+$, define the function $g_\V : \reals^\Y \to \reals_+ \cup \{-\infty\}$\raft{added $-\infty$ and changed the domain, since the definition implies that $x$ could be outside of $\reals^\Y_+$, as otherwise you wouldn't need the indicator} by
  \begin{align*}
    g_\V(x) = \inf_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~. % = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~.~
  \end{align*}
\end{definition}
\noindent
We denote the hypograph of a function $g:\reals^\Y\to\reals\cup\{-\infty\}$ by $\hyp(g) = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y \times \reals$.

@@

Using the polyhedral perspective above, we can characterize the hypograph of $\risk L_+ = g_{L(\R)}$ and extract a \emph{finite} set $\V$ of ``active'' loss vectors, so that $\risk L_+ = g_\V$.
%Let $\H_{L(\R)} = \{H_v^+ \mid v\in L(\R)\}$.
Observe that $L(\R)$ and $\H_{L(\R)}$ may be infinite sets.  
%We find the existence of a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$, and proceed to work with such a $\V$.
\begin{claim}\label{claim:gV-equals-riskL}
	Suppose we are given a minimizable $L : \R \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$.
	Then $\hyp(g_{L(\R)}) = \cap(\H_\Y \cup \H_{L(\R)})$.
	Moreover, there is a finite $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_{\V}$. %$\hyp(g_{L(\R)}) = \cap (\H_{\V} \cup \H_\Y) = \hyp(g_{\V})$ and . 
\end{claim}
\begin{proof}
	Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
	Let $x \in \reals^\Y_+$.
	\begin{align*}
	(x,c) \in \hyp(g_{L(\R)})
	&\iff g_{L(\R)}(x) \geq c & \text{definition of hypograph}\\
	&\iff \risk L_+(x) \geq c & \text{$g_{L(\R)}=\risk L_+$}\\
    &\iff \inprod{v}{x} \geq c \,\, \forall v \in {L(\R)} & \text{definition of $\risk L_+$, minimizability} \\
    % as the infimum % over $v \in {L(\R)}$ of}\\
    % & & \text{the inner product with $x$ and minimizable;} \\
	&\iff (x,c) \in H^+_{v} \,\, \forall v \in {L(\R)} & \text{definition of $H^+_v$}\\
	&\iff (x,c) \in \cap \H_{L(\R)} & 
	\end{align*}
	Combining the two equalities, we have $\hyp(g_{L(\R)}) = \cap (\H_\Y \cup \H_{L(\R)})$.
	The existence of a finite $\V \subseteq {L(\R)}$ follows as $\risk L_+$ polyhedral implies $\hyp(\risk L_+)$ is a polyhedron, which has a finite representation by definition. \jessiet{Omitting details on why $\V \subseteq {L(\R)}$.}
	%Finally, $\hyp(\risk L_+) = \hyp(g_{L(\R)}) = \hyp(g_{\V})$ if and only if $\risk L_+ = g_{L(\R)} = g_{\V}$. 
\end{proof}

@@

The previous claim allows us to proceed while considering the finite set $\V$ rather than the full range $L(\R)$.
In particular, the finiteness of $\V$ gives us a finite halfspace representation $\H$ with which to apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
The unique smallest halfspace representation $\H^*\subseteq\H$ will then correspond to a unique $\V^*\subseteq\V$.

\begin{lemma}\label{lem:G-unique-facets-Hstar}
  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$.
  %\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
  There is some unique irredundant $\H^* \subseteq \H$ such that $\hyp(g_\V) = \cap \H^*$. 
  Moreover, for each $H^+ \in\H^*$ and $H$ such that $H = \partial H^+$, the face $\hyp(g_\V) \cap H$ is a facet. 
  Moreover, $\H_\Y \subseteq \H^*$. 
\end{lemma}
\begin{proof}
	First, we need to show that $\hyp(g_\V)$ is full-dimensional.
	Since $g_\V$ is nonnegative on $\reals_+^\Y$, $\hyp(g_\V)$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.

@@

\begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
  Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ given by Lemma~\ref{lem:G-unique-facets-Hstar}. %such that $\hyp(g_\V) = \cap \H^*$.
  Then
  (i) There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  (ii) $F_v$ is a facet of $\hyp(g_\V)$ for each $v\in\V^*$.\raft{Is $F_v$ defined?  Looks like it got cut (we were going to move it to this subsec maybe)}
  (iii) $\V^* \subseteq \V$.
  (iv) $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y) = g_{\V^*}(x)$.
\end{corollary}
\begin{proof}
%  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
%
  (i) Since $\hyp(g_\V)$ is full-dimensional, the facets of $\hyp(g_\V)$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $H^+ \in \H^*$\raft{was ``$\H^* = \{H^+\}$''} by Lemma~\ref{lem:G-unique-facets-Hstar}.
  Any facet must then be some intersection of an $H_y \cap \hyp(g_\V)$ or $H_v \cap \hyp(g_\V)$.
  Since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}, take $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$.
  (ii) Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v$ of $\hyp(g_\V)$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
%
%  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Lemma~\ref{lem:G-unique-facets-Hstar}.
  (iii)  $\H_\Y \cup \H_{\V^*} = \H^*$ by (i), and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:G-unique-facets-Hstar}, ergo $\V^* \subseteq \V$.
  (iv)   The result holds if $\hyp(g_\V) = \hyp(g_{\V^*})$.
  By construction, $\hyp(g_\V) = \cap (\H_\Y \cup \H_\V)= \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$ where the first equality follows as $\H^* \subseteq \H$.
  Thus $g_\V$ can be written as $g_\V(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+) = g_{\V^*}(x)$. 
\end{proof}

@@

The above establishes our primary assumption for the rest of this section.

\begin{assumption}\label{assum:V-star-exists-infinite}
	$L : \R \to \reals^\Y_+$ is a minimizable loss function such that $\risk L_+ = g_{L(\R)}$ is polyhedral.
	%$\V \subseteq L(\R)$ is a finite set such that $g_\V = g_{L(\R)}$.
	$\V^* \subseteq L(\R)$ is the unique finite set such that $g_{L(\R)} = g_{\V^*}$ and $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap(\H_{\V^*} \cup \H_\Y)$, and $\H_{\V^*} \cup \H_\Y$ is irredundant.
\end{assumption}

\begin{proposition}\label{prop:poly-risk-assumption-satisfied}
	Given a minimizable loss $L : \R \to \reals^\Y_+$ such that $\risk L_+$ is polyhedral, there exists a finite $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
\end{proposition}
\begin{proof}
	Given $L$ with polyhedral $\risk L_+$, Claim~\ref{claim:gV-equals-riskL} gives a finite set $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_\V$. 
	Now consider the unique $\V^* \subseteq \V \subseteq L(\R)$ that is given in Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $g_{L(\R)} = g_\V = g_{\V^*}$.
	Finally, by construction in Lemma~\ref{lem:G-unique-facets-Hstar}, we additionally have $\H^* = \H_\Y \cup \H_{\V^*}$, and $\H^*$ is irredundant.
%	WTS
%	(i) $\V^* \subseteq L(\R)$ -- done
%	(ii) $\V^*$ unique and smallest
%	(iii) $g_{L(\R)} = g_{\V^*}$
%	(iv) $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap (\H_{\V^*} \cup \H_\Y)$
\end{proof}
